NumPy---Array Programming in Python

### 2020-01-31 body.tex
Edit additions to proliferation section

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{static/sketches/array-concepts}   
  \caption{\textbf{Fundamental Array Concepts.}
    \textbf{a,} The NumPy array data structure and its associated metadata fields.
    \textbf{b,} Indexing an array with various types of arguments.
    \textbf{c,} Indexing with arrays, which broadcast the indexing arguments before performing the lookup.
    \textbf{d,} Broadcasting in scalar addition, and in the division of two-dimensional arrays.
    \textbf{e,} Reduction operations act along one or more axes. In this
    example, a three-dimensional array is shown to be summed along various single
    axes to produce two-dimensional results, or along two axes consecutively to
    produce a one-dimensional result.
   }
  \label{fig:array-concepts}
\end{figure*}

@@

NumPy provides in-memory, multidimensional, homogeneously typed
(i.e., single pointer and strided) arrays on CPUs.
It runs on machines ranging from embedded devices up to the worlds
largest supercomputers [citation needed] and provides a performance
which often approaches compiled languages.
When algorithms do not fit the array programming approach,
or require a faster implementation,
a number of tools (e.g. Cython, Numba, Pythran, ...)
are available to transparently accelerate crucial parts.
These tools allow for a high level array orientated code base without sacrificing
the speed expected from a compiled language.
In many cases fast algorithms are implemented by libraries in the scientific
python ecosystem so that most user programs are sufficiently fast being
written in Python and NumPy.
% smooth experience/intengration from high level <-> low level?

>>>>

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{static/sketches/array-concepts}   
  \caption{\textbf{Fundamental Array Concepts.}
    \textbf{a,} The NumPy array data structure and its associated metadata fields.
    \textbf{b,} Indexing an array with various types of arguments.
    \textbf{c,} Indexing with arrays, which broadcast the indexing arguments before performing the lookup.
    \textbf{d,} Vectorization efficiently applies operations to groups of elements
    \textbf{e,} Broadcasting in scalar addition, and in the division of two-dimensional arrays.
    \textbf{e,} Reduction operations act along one or more axes. In this
    example, a three-dimensional array is shown to be summed along various single
    axes to produce two-dimensional results, or along two axes consecutively to
    produce a one-dimensional result.
   }
  \label{fig:array-concepts}
\end{figure*}

@@

NumPy provides in-memory, multidimensional, homogeneously typed
(i.e., single pointer and strided) arrays on CPUs.
It runs on machines ranging from embedded devices to the world's
largest supercomputers \fixme{citation needed} and yields performance
approaching that of compiled languages.
For algorithms that do not fit the array programming approach,
or require even faster implementations, a variety of tools exist (Cython, Numba, or Pythran, ...) that transparently accelerates bottlenecks.
These tools allow programmers to express concepts using high level array programming without sacrificing efficiency.
In many cases, fast algorithms already are implemented by libraries in the scientific Python ecosystem; using these primitives, efficient codes can be written in pure Python.
% smooth experience/intengration from high level <-> low level?
